Analytic reproducibility in articles receiving open data badges at Psychological Science: An observational assessment

### 2020-07-09 manuscript/manuscript.Rmd
updated code ocean link

Although journal policy is potentially helpful for incentivisation and verification, the reproducibility of a scientific manuscript is fundamentally under the control of its authors. Fortunately, a variety of tools are now available that allow for the writing of entirely reproducible research reports in which data, analysis code, and prose are intrinsically linked [e.g., @vuorre2020]. It should be noted that ensuring the reproducibility of a scientific manuscript requires a non-trivial time investment and presently, there is room for improvement in the data management and analysis practices adopted by psychology researchers [e.g., @borghi2020]. Continued development of user-friendly tools that facilitate reproducibility and dedicated reproducibility training may help to reduce this burden. Additionally, the costs of ensuring reproducibility could be offset by the benefits of improved workflow efficiency, error detection and mitigation, and opportunities for data re-use. Detailed guidance on data sharing, data management, and analytic reproducibility is available to support psychological scientists seeking to improve these practices in their own research [@klein2018]. The present manuscript is an illustration of these practices in action (https://doi.org/10.24433/CO.6557927.v1).

@@

The study protocol (hypotheses, methods, and analysis plan) was pre-registered on October 18, 2017 (https://osf.io/2cnkq/). All deviations from this protocol or additional exploratory analyses are explicitly acknowledged in Supplementary Information \@ref(prereg). All data exclusions and measures conducted during this study are reported. All data (https://osf.io/qzmpj/), materials (https://osf.io/awxt6/), and analysis scripts (https://osf.io/vwzn4/) related to this study are publicly available on the Open Science Framework. To facilitate reproducibility this manuscript was written by interleaving regular prose and analysis code using knitr [@R-knitr] and papaja [@R-papaja], and is available in a Code Ocean container (https://doi.org/10.24433/CO.6557927.v1) which re-creates the software environment in which the original analyses were performed. Analysis code, reports, and Code Ocean containers are also available for each reproducibility check (https://osf.io/hf9jy/).

>>>>

Although journal policy is potentially helpful for incentivisation and verification, the reproducibility of a scientific manuscript is fundamentally under the control of its authors. Fortunately, a variety of tools are now available that allow for the writing of entirely reproducible research reports in which data, analysis code, and prose are intrinsically linked [e.g., @vuorre2020]. It should be noted that ensuring the reproducibility of a scientific manuscript requires a non-trivial time investment and presently, there is room for improvement in the data management and analysis practices adopted by psychology researchers [e.g., @borghi2020]. Continued development of user-friendly tools that facilitate reproducibility and dedicated reproducibility training may help to reduce this burden. Additionally, the costs of ensuring reproducibility could be offset by the benefits of improved workflow efficiency, error detection and mitigation, and opportunities for data re-use. Detailed guidance on data sharing, data management, and analytic reproducibility is available to support psychological scientists seeking to improve these practices in their own research [@klein2018]. The present manuscript is an illustration of these practices in action (https://doi.org/10.24433/CO.1796004.v1).

@@

The study protocol (hypotheses, methods, and analysis plan) was pre-registered on October 18, 2017 (https://osf.io/2cnkq/). All deviations from this protocol or additional exploratory analyses are explicitly acknowledged in Supplementary Information \@ref(prereg). All data exclusions and measures conducted during this study are reported. All data (https://osf.io/qzmpj/), materials (https://osf.io/awxt6/), and analysis scripts (https://osf.io/vwzn4/) related to this study are publicly available on the Open Science Framework. To facilitate reproducibility this manuscript was written by interleaving regular prose and analysis code using knitr [@R-knitr] and papaja [@R-papaja], and is available in a Code Ocean container (https://doi.org/10.24433/CO.1796004.v1) which re-creates the software environment in which the original analyses were performed. Analysis code, reports, and Code Ocean containers are also available for each reproducibility check (https://osf.io/hf9jy/).
